Construction of Chebyshev nets with singularities

### 2017-07-07 Article.tex
Nettoyage section 4.1

\section{Existence of a Chebyshev net from Cauchy boundary conditions}
\label{sec:chap4}
\subsection{Statement of the main result}
Let 
\begin{equation*}
  D=[0,L_u]\Times[0,L_v],\quad\text{with } L_u,L_v\in\R_\ast^+,
\end{equation*}
 and let $\gamma_u:[0,L_u]\to\surf$ and $\gamma_v:[0,L_v]\to\surf$ be
 two curves such that $\gamma_u(0)=\gamma_v(0)$, and forming an
 interior angle $\angle(\gamma_u'(0),\gamma_v'(0))\in(0,\pi)$ at their
 intersection and exterior angle
 $\psi=\pi-\angle(\gamma_u'(0),\gamma_v'(0))$. For clarity of
 exposition, throughout this section, we consider a slightly different
 notion of Chebyshev net which will refer to mappings (not necessarily
 homeomorphisms) $\varphi:D\to\surf$ satisfying
\begin{subequations}\label{eq:cheb-def-c3}
\begin{align}\label{eq:cheb-def-c3a}
|\partial_u \varphi|_g(u,v) = 1,\\
|\partial_v \varphi|_g(u,v) = 1,\label{eq:cheb-def-c3b}
\end{align}
\end{subequations}
for all $(u,v)\in D$. Furthermore, note that the orientation of the boundary curve $\gamma_v$ is reversed in this section to simplify the exposition. 
We prove in the sequel the existence and the uniqueness of a Chebyshev net $\varphi:D\to\surf$ verifying the Cauchy boundary conditions
\begin{equation}\label{eq:cond-bord-c3}
\begin{split}
  \varphi(u,0)=\gamma_u(u),\quad\forall u\in[0,L_u],\\ 
  \varphi(0,v)=\gamma_v(v),\quad\forall v\in[0,L_v].
\end{split}
\end{equation}
Since $\surf$ is a plane immersion, we identify in the sequel $\surf=(\R^2,g)$. We moreover suppose that the metric $g$ satisfies the following property: for all compact set $W\subset\surf$, there exists $\Csurf>1$ such that 
\begin{equation}\label{eq:equiv}
  |X|_{g(p)} \leq \Csurf|X|,
\end{equation}
for all $p\in W$ and $X\in\R^2$. Unless explicitly mentionned, all the considered curves are assumed to be arc-length parametrized. Then, the geodesic curvature $\ko_{\sigma}:I\subset\R\to\R$ of a curve $\sigma:I\to\surf$ is defined by
\begin{equation}\label{eq:geod-dual1}
   \ko_{\sigma} = \langle\sigma^{\prime\prime},\sigma^{\prime\perp}\rangle_g,
\end{equation}
where $\sigma^{\prime\perp}$ is the direct $\frac{\pi}{2}$-rotation of $\sigma'$. In the sequel, $C$ and $\tilde C$ are two generic constants whose values can change at each occurrence and we will often explicit their dependence.

Following \cite{Ghys09}, we reformulate the problem of finding a Chebyshev net $\varphi:D\to\surf$ as the problem of finding the angle distribution $\omega:D\to\R/2\pi\Z$ between the coordinate curves defined by $\omega(u,v) = \angle(\DU\varphi, \DV\varphi)(u,v)$. With this purpose in mind, we observe that $\omega$ satisfies the following integrability condition (in the form of a modified Sine-Gordon equation) \cite{Ghys09}
\begin{equation}  \label{eq:cond-integr}
  \DUV \omega = -K(\varphi) \sin(\omega).
Equivalently, $\omega$ satisfies the integrated form of \eqref{eq:cond-integr} called the Hazzidakis formula
\begin{equation}  \label{eq:hazz-form}
 \omega(u,v) =& ~~\angle\big(\gamma_u'(0),\gamma_v'(0)\big) - \int_0^u \ko_u(s)ds +
  \int_{0}^v\ko_v(s)ds\\
& - \int_0^u\int_0^vK(\varphi(s,t))\sin\big[\omega(s,t)\big]ds~dt,
for all $(u,v)\in D$, with $\ko_u:[0,L_u]\to\R$ and $\ko_v:[0,L_v]\to\R$ the geodesic curvatures of $\gamma_u$ and $\gamma_v$ respectively (see Figure \ref{fig:hazz-primal-c4}). 
  \begin{tikzpicture}[x=1cm,y=1cm]
    \pgfmathsetmacro{\cos}{cos(deg(60))}
    \pgfmathsetmacro{\sin}{sin(deg(60))}
    \draw[thick] (0,0) arc[start angle=150,delta angle=-30,radius=13.66] coordinate[pos=0.2] (u1) coordinate[pos=0.4] (u2) coordinate[pos=0.6] (u3) coordinate[pos=0.8] (u4);
    \coordinate (umid) at (2.3,2.7);
    \draw (umid) node[anchor=west]{$\varphi(\cdot,0){=}\gamma_u$};
    \draw[thick] (0,0) arc[start angle=-120,delta angle=-30,radius=13.66] coordinate[pos=0.2] (v1) coordinate[pos=0.4] (v2) coordinate[pos=0.6] (v3) coordinate[pos=0.8] (v4);
    \coordinate (vmid) at (-2.9,2.);
    \draw (vmid) node[anchor=east,inner sep=0pt]{$\varphi(0,\cdot){=}\gamma_v$};
   \draw[dotted] (u1) arc[start angle=-120,delta angle=-25,radius=13.66];
   \draw[dotted] (u2) arc[start angle=-120,delta angle=-20,radius=13.66];
   \draw[dotted] (u3) arc[start angle=-120,delta angle=-15,radius=13.66] coordinate[pos=0.8] (uv);
   \draw[dotted] (u4) arc[start angle=-120,delta angle=-10,radius=13.66];
   \draw[dotted] (v1) arc[start angle=150,delta angle=-25,radius=13.66];
   \draw[dotted] (v2) arc[start angle=150,delta angle=-20,radius=13.66];
   \draw[dotted] (v3) arc[start angle=150,delta angle=-15,radius=13.66];
   \draw[dotted] (v4) arc[start angle=150,delta angle=-10,radius=13.66];
   \draw[latex-] ($(uv)+(-42:0.5)$) arc[start angle=-42,delta angle=-96,radius=0.5];
   \draw ($(uv)+(-90:0.5)$) node[anchor=north]{$\omega(u,v)$};
 %   \draw[-latex] (0,0) -- (-30:1);
%    \draw ($(0,0)+(-45:0.4)$) node[anchor=north]{$\eta_1'(0)$};
 %   \draw[-latex] (0,0) -- (60:1);
%    \draw ($(0,0)+(130:0.9)$) node[anchor=west, inner sep=1pt]{$\eta_2'(0)$};
%    \draw[-latex] ($(0,0)+(-30:0.5)$) arc[start angle=-30, delta angle=90, radius=0.5];
%    \draw ($(0,0)+(15:0.5)$) node[anchor=west]{$\psi{=}\pi{-}\omega(0,0)$};
    \pgfmathsetmacro{\r}{0.5}
    \draw[-latex] (60:\r) arc[start angle=60, delta angle=90, radius=\r];
    \draw ($(90:.7)+(-.2,0)$) node{$\omega(0,0)$};
  \caption{Illustration of the coordinate curves of a Chebyshev net $\varphi$}\label{fig:hazz-primal-c4}
We moreover remark that, since $\varphi$ is a Chebyshev net, it satisfies the following property:
\begin{subequations}\label{eq:courb-geod}
\begin{align}\label{eq:courb-geoda}
\kop_u(u,v) &= -\partial_u\omega(u,v), \\\label{eq:courb-geodb}
\kop_v(u,v) &= \partial_v\omega(u,v),
for all $(u,v)\in D$, where $\kop_u:D\to\R$ and $\kop_v:D\to\R$ are respectively the geodesic curvatures of the $u$-coordinate curves and of the $v$-coordinate curves of $\varphi$. We obtain by combining \eqref{eq:cond-bord-c3} and \eqref{eq:courb-geod} that the angle distribution $\omega$ satisfies the boundary conditions
\begin{subequations}\label{eq:cond-bord-angle}
\omega(u, 0) &= \angle(\gamma_u'(0), \gamma_v'(0)) - \int_0^u\ko_u(s)\ds,\quad\forall u\in[0,L_u],\\
\omega(0,v) &= \angle(\gamma_u'(0), \gamma_v'(0)) + \int_0^v\ko_v(s)\ds,\quad\forall v\in[0,L_v].
We will first show that we can associate with any angle distribution $\omega:D\to(0,\pi)$ satisfying \eqref{eq:cond-bord-angle} a unique mapping $\varphi:=\I(\gamma,\omega):D\to\surf$ satisfying \eqref{eq:cheb-def-c3b}, \eqref{eq:cond-bord-c3}, and \eqref{eq:courb-geodb}, and then we will show that this mapping also satisfies \eqref{eq:cheb-def-c3a} and \eqref{eq:courb-geoda} whenever $\omega$ satisfies the integrability condition \eqref{eq:cond-integr}. This section aims at proving the following result:
\begin{theorem}[Existence and uniqueness of Chebyshev nets]\label{thm2inexact}
Let $\surf$ be a smooth, open, complete, and simply connected
surface. Let $\gamma_u:\R^+\to\surf$ and $\gamma_v:\R^+\to\surf$ be
two smooth curves with respective geodesic curvatures $\ko_u:\R^+\to\R$ and
$\ko_v:\R^+\to\R$, and such that $\gamma_u(0) = \gamma_v(0)$. Suppose
that $\psi=\pi-\angle(\gamma_u'(0),\gamma_v'(0))\in(0,\pi)$ and that
the sector $\Omega$ delimited by $\gamma_u$ and $\gamma_v$
verifies \[\int_{\gamma_u}{\ko_u^+} + \int_{\gamma_v}{\ko_v^-} +
\int_{\Omega}{K^+}<\pi-\psi \text{ and } \int_{\gamma_u}{\ko_u^-} +
\int_{\gamma_v}{\ko_v^+} + \int_{\Omega}{K^-}<\psi.\] Let
$L_u,L_v\in\R_\ast^+$ and $D=[0,L_u]\Times[0,L_v]$. Then, there exists
a unique angle distribution $\omega:D\to(o,\pi)$ verifying the
boundary conditions \eqref{eq:cond-bord-angle} and satisfying the
Hazzidakis formula \eqref{eq:hazz-form}, with
$\varphi:=\I(\gamma,\omega): D\to\surf$ the unique mapping satisfying
\eqref{eq:cheb-def-c3b}, \eqref{eq:cond-bord-c3} and
\eqref{eq:courb-geodb}. The mapping $\varphi$ is a smooth Chebyshev net on
$\Omega$ with angles $0<\omega<\pi$.
In the previous statement, we have not defined precisely the regularity of the objects or the norms on the considered vector spaces. These are defined in Section \ref{sec:norms}, and a more accurate statement of Theorem \ref{thm2inexact} is given by Theorem \ref{thm2}. A direct consequence of Theorem \ref{thm2} is the following theorem:
\begin{theorem}[Existence of a unique solution to integrability condition]
  Let $\surf$ be a smooth, open, complete, and simply connected surface. Let $\gamma_u:[0,L_u]\to\surf$, with $L_u\in\R_\ast^+\cup\{\infty\}$, and $\gamma_v:[0,L_v]\to\surf$, with $L_v\in\R_\ast^+\cup\{\infty\}$, be two smooth curves with respective geodesic curvatures $\ko_u:[0,L_u]\to\R$ and $\ko_v:[0,L_v]\to\R$, and such that $\gamma_u(0) = \gamma_v(0)$. Suppose that $\angle(\gamma_u'(0),\gamma_v'(0))\in(0,\pi)$. Then, there exists a unique angle distribution $\omega:D\to\R/2\pi\Z$, with $D=[0,L_u]\Times [0,L_v]$, verifying the boundary conditions \eqref{eq:cond-bord-angle} and satisfying the Hazzidakis formula \eqref{eq:hazz-form}, with $\varphi:=\I(\gamma,\omega): D\to\surf$ the unique mapping satisfying \eqref{eq:cheb-def-c3b}, \eqref{eq:cond-bord-c3} and \eqref{eq:courb-geodb}.

  Suppose moreover that there exists $\tilde D=[0,\tilde L_u]\Times[0,\tilde L_v]$, with $\tilde L_u\in(0,L_u]$ and $\tilde L_v\in(0,L_v]$, such that $0<\omega(u,v)<\pi$, for all $(u,v)\in \tilde D$. Then, the mapping $\varphi\big|_{\tilde D}$ is a Chebyshev nets, that is, it satisfies \eqref{eq:cheb-def-c3} for all $(u,v)\in \tilde D$.
\end{theorem}

In order to prove Theorem \ref{thm2}, we proceed along the following plan. In Section \ref{subsec:constr-param}, given the two curves $\gamma_u$ and $\gamma_v$ on $\surf$ and the angle distribution $\omega:D\to\R/2\pi\Z$ between the coordinate curves, we first construct the candidate Chebyshev net $\varphi=\I(\gamma,\omega):D\to\surf$. We then show that whenever $\varphi$ satisfies the integrability condition \eqref{eq:cond-integr}, this mapping also satisfies \eqref{eq:cheb-def-c3} under suitable regularity conditions.  In Section \ref{subsec:exist-pt-fixe}, we view the Hazzidakis formula \eqref{eq:hazz-form}, with $\varphi:=\I(\gamma,\omega)$, as a fixed-point problem on $\omega$. We show existence and uniqueness of the solution to this fixed-point equation for the curves $\gamma_u$ and $\gamma_v\big|_{[0,L_0]}:[0,L_0]\to\surf$, where $L_0\in(0,L_v]$ is a constant depending on the $C^0$-norm of the geodesic curvatures of $\gamma_u$ and $\gamma_v$. This result is called ``local existence'' in what follows. We finally extend this result to the curves $\gamma_u$ and $\gamma_v$ of arbitrary length, in the spirit of the Cauchy--Lipschitz theorem.

@@

In this step, the domain of definition of the two-dimensional variables for the different norms is always $D_L=[0,L_u]\Times[0,L]$ and will not be specified. In all the subsequent estimates, unless explicitly mentionned, the constants only depend on $\RR(\gamma)$ and $\RR(\sigma)$. We set $\varphi_\sigma := \I(\sigma,\omega_\sigma)\in\Phi^{1,2}$ and we denote $\ko_{u,2}\in C^0([0,L_u])$ and $\ko_{v,2}\in C^0([0,L_v])$ the geodesic curvatures of $\sigma_u$ and $\sigma_v$, respectively. First, we prove that

>>>>

\section{Existence of a Chebyshev net from Cauchy boundary conditions}
\label{sec:chap4}
\subsection{Statement of the main result}
Let 
\begin{equation*}
  D=[0,L_u]\Times[0,L_v],\quad\text{with } L_u,L_v\in\R_\ast^+,
\end{equation*}
 and let $\gamma_u:[0,L_u]\to\surf$ and $\gamma_v:[0,L_v]\to\surf$ be
 two curves such that $\gamma_u(0)=\gamma_v(0)$, and forming an
 interior angle $\angle(\gamma_u'(0),\gamma_v'(0))\in(0,\pi)$ at their
 intersection and exterior angle
 $\psi=\pi-\angle(\gamma_u'(0),\gamma_v'(0))$. For clarity of
 exposition, throughout this section, we consider a slightly different
 notion of Chebyshev net which will refer to mappings (not necessarily
 homeomorphisms) $\varphi:D\to\surf$ satisfying
\begin{subequations}\label{eq:cheb-def-c3}
\begin{align}\label{eq:cheb-def-c3a}
|\partial_u \varphi|_g(u,v) = 1,\\
|\partial_v \varphi|_g(u,v) = 1,\label{eq:cheb-def-c3b}
\end{align}
\end{subequations}
for all $(u,v)\in D$. Furthermore, note that the orientation of the boundary curve $\gamma_v$ is reversed in this section to simplify the exposition. 
We prove in the sequel the existence and the uniqueness of a Chebyshev net $\varphi:D\to\surf$ verifying the Cauchy boundary conditions
\begin{equation}\label{eq:cond-bord-c3}
\begin{split}
  \varphi(u,0)=\gamma_u(u),\quad\forall u\in[0,L_u],\\ 
  \varphi(0,v)=\gamma_v(v),\quad\forall v\in[0,L_v].
\end{split}
\end{equation}
Since $\surf$ is a plane immersion, and since $\int_\surf{K^+}<2\pi$
and $\int_\surf{K^-}<\infty$, there exists a global bi-Lipschitz
parametrization of $\surf$~\cite{Bonk03}. In the sequel, we identify
$\surf=(\R^2,g)$. The metric $g$ satisfies the following property:
there exists $\Csurf>1$ such that for all $X\in\R^2$,
\begin{equation}\label{eq:equiv}
  \frac{1}{\Csurf}|X|\leq |X|_{g} \leq \Csurf|X|.
\end{equation}
Unless explicitly mentioned, all the considered curves are assumed to be arc-length parametrized. In the sequel, $C$ and $\tilde C$ are two generic constants whose values can change at each occurrence and we will often explicit their dependence.

Following \cite{Ghys09}, we reformulate the problem of finding a Chebyshev net $\varphi:D\to\surf$ as the problem of finding the angle distribution $\omega:D\to(0,\pi)$ between the coordinate curves defined by $\omega(u,v) = \angle(\DU\varphi, \DV\varphi)(u,v)$. With this purpose in mind, we observe that $\omega$ satisfies the following integrability condition (in the form of a modified Sine-Gordon equation) \cite{Ghys09}
\begin{equation}  \label{eq:cond-integr}
  \DUV \omega = -K(\varphi) \sin(\omega).
\end{equation}
Equivalently, $\omega$ satisfies the integrated form of \eqref{eq:cond-integr} called the Hazzidakis formula
\begin{multline}  \label{eq:hazz-form}
 \omega(u,v) = \angle\big(\gamma_u'(0),\gamma_v'(0)\big) - \int_0^u \ko_u(s)ds +
  \int_{0}^v\ko_v(s)ds\\
 - \int_0^u\int_0^vK(\varphi(s,t))\sin\big[\omega(s,t)\big]ds~dt,
\end{multline} 
for all $(u,v)\in D$, with $\ko_u:[0,L_u]\to\R$ and $\ko_v:[0,L_v]\to\R$ the geodesic curvatures of $\gamma_u$ and $\gamma_v$ respectively (see Figure \ref{fig:hazz-primal-c4}). 
\begin{figure}[!htp]
  \centering
  \begin{tikzpicture}[x=1cm,y=1cm]
    \pgfmathsetmacro{\cos}{cos(deg(60))}
    \pgfmathsetmacro{\sin}{sin(deg(60))}
    \draw[thick] (0,0) arc[start angle=150,delta angle=-30,radius=13.66] coordinate[pos=0.2] (u1) coordinate[pos=0.4] (u2) coordinate[pos=0.6] (u3) coordinate[pos=0.8] (u4);
    \coordinate (umid) at (2.3,2.7);
    \draw (umid) node[anchor=west]{$\varphi(\cdot,0){=}\gamma_u$};
    \draw[thick] (0,0) arc[start angle=-120,delta angle=-30,radius=13.66] coordinate[pos=0.2] (v1) coordinate[pos=0.4] (v2) coordinate[pos=0.6] (v3) coordinate[pos=0.8] (v4);
    \coordinate (vmid) at (-2.9,2.);
    \draw (vmid) node[anchor=east,inner sep=0pt]{$\varphi(0,\cdot){=}\gamma_v$};
   \draw[dotted] (u1) arc[start angle=-120,delta angle=-25,radius=13.66];
   \draw[dotted] (u2) arc[start angle=-120,delta angle=-20,radius=13.66];
   \draw[dotted] (u3) arc[start angle=-120,delta angle=-15,radius=13.66] coordinate[pos=0.8] (uv);
   \draw[dotted] (u4) arc[start angle=-120,delta angle=-10,radius=13.66];
   \draw[dotted] (v1) arc[start angle=150,delta angle=-25,radius=13.66];
   \draw[dotted] (v2) arc[start angle=150,delta angle=-20,radius=13.66];
   \draw[dotted] (v3) arc[start angle=150,delta angle=-15,radius=13.66];
   \draw[dotted] (v4) arc[start angle=150,delta angle=-10,radius=13.66];
   \draw[latex-] ($(uv)+(-42:0.5)$) arc[start angle=-42,delta angle=-96,radius=0.5];
   \draw ($(uv)+(-90:0.5)$) node[anchor=north]{$\omega(u,v)$};
 %   \draw[-latex] (0,0) -- (-30:1);
%    \draw ($(0,0)+(-45:0.4)$) node[anchor=north]{$\eta_1'(0)$};
 %   \draw[-latex] (0,0) -- (60:1);
%    \draw ($(0,0)+(130:0.9)$) node[anchor=west, inner sep=1pt]{$\eta_2'(0)$};
%    \draw[-latex] ($(0,0)+(-30:0.5)$) arc[start angle=-30, delta angle=90, radius=0.5];
%    \draw ($(0,0)+(15:0.5)$) node[anchor=west]{$\psi{=}\pi{-}\omega(0,0)$};
    \pgfmathsetmacro{\r}{0.5}
    \draw[-latex] (60:\r) arc[start angle=60, delta angle=90, radius=\r];
    \draw ($(90:.7)+(-.2,0)$) node{$\omega(0,0)$};
  \end{tikzpicture}
  \caption{Illustration of the coordinate curves of a Chebyshev net $\varphi$}\label{fig:hazz-primal-c4}
\end{figure}

Moreover, remark that, since $\varphi$ is a Chebyshev net, it satisfies the following property:
\begin{subequations}\label{eq:courb-geod}
\begin{align}\label{eq:courb-geoda}
\kop_u(u,v) &= -\partial_u\omega(u,v), \\\label{eq:courb-geodb}
\kop_v(u,v) &= \partial_v\omega(u,v),
\end{align}
\end{subequations}
for all $(u,v)\in D$, where $\kop_u:D\to\R$ and $\kop_v:D\to\R$ are respectively the geodesic curvatures of the $u$-coordinate curves and of the $v$-coordinate curves of $\varphi$. We obtain by combining \eqref{eq:cond-bord-c3} and \eqref{eq:courb-geod} that the angle distribution $\omega$ satisfies the boundary conditions
\begin{subequations}\label{eq:cond-bord-angle}
\begin{align}
\omega(u, 0) &= \angle(\gamma_u'(0), \gamma_v'(0)) - \int_0^u\ko_u(s)\ds,\quad\forall u\in[0,L_u],\\
\omega(0,v) &= \angle(\gamma_u'(0), \gamma_v'(0)) + \int_0^v\ko_v(s)\ds,\quad\forall v\in[0,L_v].
\end{align}
\end{subequations}
We first show that we can associate to any angle distribution
$\omega:D\to(0,\pi)$ satisfying \eqref{eq:cond-bord-angle} a unique
mapping $\varphi:=\I(\gamma,\omega):D\to\surf$ satisfying
\eqref{eq:cheb-def-c3b}, \eqref{eq:cond-bord-c3}, and
\eqref{eq:courb-geodb}. We then show that this mapping also satisfies
\eqref{eq:cheb-def-c3a} and \eqref{eq:courb-geoda} whenever $\omega$
satisfies the integrability condition \eqref{eq:cond-integr}. This
section aims at proving the following result:
\begin{theorem}[Existence and uniqueness of Chebyshev nets]\label{thm2full}
Let $\surf$ be a smooth, open, complete, and simply connected
surface. Let $\gamma_u:\R^+\to\surf$ and $\gamma_v:\R^+\to\surf$ be
two smooth curves with respective geodesic curvatures $\ko_u:\R^+\to\R$ and
$\ko_v:\R^+\to\R$, and such that $\gamma_u(0) = \gamma_v(0)$. Suppose
that $\psi=\pi-\angle(\gamma_u'(0),\gamma_v'(0))\in(0,\pi)$ and that
the sector $\Omega$ delimited by $\gamma_u$ and $\gamma_v$
verifies \[\int_{\gamma_u}{\ko_u^+} + \int_{\gamma_v}{\ko_v^-} +
\int_{\Omega}{K^+}<\pi-\psi \text{ and } \int_{\gamma_u}{\ko_u^-} +
\int_{\gamma_v}{\ko_v^+} + \int_{\Omega}{K^-}<\psi.\] Let
$L_u,L_v\in\R_\ast^+\cup\{+\infty\}$ and $D=[0,L_u]\Times[0,L_v]$. Then, there exists
a unique angle distribution $\omega:D\to(0,\pi)$ verifying the
boundary conditions \eqref{eq:cond-bord-angle} and satisfying the
Hazzidakis formula \eqref{eq:hazz-form}, with
$\varphi:=\I(\gamma,\omega): D\to\surf$ the unique mapping satisfying
\eqref{eq:cheb-def-c3b}, \eqref{eq:cond-bord-c3} and
\eqref{eq:courb-geodb}. The mapping $\varphi$ is a smooth Chebyshev net on
$\Omega$ with angles $0<\omega<\pi$.
\end{theorem}

In order to prove Theorem \ref{thm2full}, we proceed along the following plan. In Section \ref{subsec:constr-param}, given the two curves $\gamma_u$ and $\gamma_v$ on $\surf$ and the angle distribution $\omega:D\to\R/2\pi\Z$ between the coordinate curves, we first construct the candidate Chebyshev net $\varphi=\I(\gamma,\omega):D\to\surf$. We then show that whenever $\varphi$ satisfies the integrability condition \eqref{eq:cond-integr}, this mapping also satisfies \eqref{eq:cheb-def-c3} under suitable regularity conditions.  In Section \ref{subsec:exist-pt-fixe}, we view the Hazzidakis formula \eqref{eq:hazz-form}, with $\varphi:=\I(\gamma,\omega)$, as a fixed-point problem on $\omega$. We show existence and uniqueness of the solution to this fixed-point equation for the curves $\gamma_u$ and $\gamma_v\big|_{[0,L_0]}:[0,L_0]\to\surf$, where $L_0\in(0,L_v]$ is a constant depending on the $C^0$-norm of the geodesic curvatures of $\gamma_u$ and $\gamma_v$. This result is called ``local existence'' in what follows. We finally extend this result to the curves $\gamma_u$ and $\gamma_v$ of arbitrary length, in the spirit of the Cauchy--Lipschitz theorem.

@@

In this step, the domain of definition of the two-dimensional variables for the different norms is always $D_L=[0,L_u]\Times[0,L]$ and will not be specified. In all the subsequent estimates, unless explicitly mentioned, the constants only depend on $\RR(\gamma)$ and $\RR(\sigma)$. We set $\varphi_\sigma := \I(\sigma,\omega_\sigma)\in\Phi^{1,2}$ and we denote $\ko_{u,2}\in C^0([0,L_u])$ and $\ko_{v,2}\in C^0([0,L_v])$ the geodesic curvatures of $\sigma_u$ and $\sigma_v$, respectively. First, we prove that
